Resubmission file

### 2021-01-12 cover letter/resubmission.tex
table of contents, IDs, ijcai20 paper

\title{Resubmission file}
\subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
\author{Submission ID: TODO}
\date{}
\hypersetup{
	pdfsubject={Cover letter},
	pdfkeywords={elicitation},
}

@@

@@

\medskip
We have submitted this article for the first time to IJCAI 2020 (TODO ID?). The submission was evaluated by four reviewers; the overall assessment (full reviews are included in Section \ref{sec:reviews-ijcai}) were: 
\begin{itemize}
\item R1: Accept {\em (good paper, I can argue for accepting it)};
\item R2: Weak accept {\em (marginally above the acceptance theshold, rejecting it would not be that bad)};
\item R3: Weak reject {\em (marginally below the acceptance threshold, accepting it would not be that bad)}; and
\item R4:  Reject {\em (Not good enough, I can argue for rejecting it)}.
\end{itemize}

@@

\section{Submission to AAMAS-2021} 
\label{sec:reviews-aamas}
\subsection{Review 1}
\subsubsection*{Summary:}	The authors use the notion of minimax regret to guide the process of preference elicitation in an election (they elicit both the voters' preferences and the preferences of the chair regarding the scoring rule used). The authors show that the methodology of Lu and Boutilier for computing minimax regret still applies in their setting and present some experimental results.
\subsubsection*{Strengths:}	1) Minimax regret is a rather natural notion, which has not received much attention so far.
\subsubsection*{Weaknesses:}
1) The theoretical results are relatively simple extensions of the results of Lu and Boutilier
\newline 2) The experimental results seem quite preliminary.

@@

\section{Rejected paper AAMAS 2021}
You will find here below the version of this article that was submitted to AAMAS 2021.
%\includepdf[pages=-]{aamas21_paper_554.pdf}
\end{document}

>>>>

\title{Resubmission file}
\subtitle{Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination}
\author{Submission ID: 3177}
\date{}
\hypersetup{
	pdfsubject={Cover letter},
	pdfkeywords={elicitation},
}

@@

\tableofcontents

@@

\medskip
We have submitted this article for the first time to IJCAI 2020 (with submission ID 7094). The submission was evaluated by four reviewers; the overall assessment (full reviews are included in Section \ref{sec:reviews-ijcai}) were: 
\begin{itemize}
\item R1: Accept {\em (good paper, I can argue for accepting it)};
\item R2: Weak accept {\em (marginally above the acceptance theshold, rejecting it would not be that bad)};
\item R3: Weak reject {\em (marginally below the acceptance threshold, accepting it would not be that bad)}; and
\item R4:  Reject {\em (Not good enough, I can argue for rejecting it)}.
\end{itemize}

@@

\section{Rejected paper IJCAI 2020}
You will find here below the version of this article that was submitted to IJCAI 2020.
\includepdf[pages=-]{ijcai20_paper_7094.pdf}

\section{Submission to AAMAS 2021} 
\label{sec:reviews-aamas}
\subsection{Review 1}
\subsubsection*{Summary:}	The authors use the notion of minimax regret to guide the process of preference elicitation in an election (they elicit both the voters' preferences and the preferences of the chair regarding the scoring rule used). The authors show that the methodology of Lu and Boutilier for computing minimax regret still applies in their setting and present some experimental results.
\subsubsection*{Strengths:}	1) Minimax regret is a rather natural notion, which has not received much attention so far.
\subsubsection*{Weaknesses:}
1) The theoretical results are relatively simple extensions of the results of Lu and Boutilier
\newline 2) The experimental results seem quite preliminary.

@@

\section{Rejected paper AAMAS 2021}
You will find here below the version of this article that was submitted to AAMAS 2021.
\includepdf[pages=-]{aamas21_paper_554.pdf}
\end{document}
